Extracting Information from AGN Variability

### 2017-03-18 Manuscript.tex
Modify Abstract to please reviewer
The reviewer has complained about how we assert things that we cannot prove.
This commit softens the language of the abstract in order to make sure that
the reviewer is no longer justified in complaining.

% Enter the current year, for the copyright statements etc.
\pubyear{2016}

@@

% Abstract of the paper
\begin{abstract}
AGN exhibit rapid, high amplitude stochastic flux variability across the entire electromagnetic spectrum on timescales ranging from hours to years. The cause of this variability is poorly understood. We present a new method for using variability to (1) measure the time-scales on which flux perturbations evolve and (2) characterize the driving flux perturbations. We model the observed light curve of an AGN as a linear differential equation driven by stochastic impulses. Physically, the impulses could be local `hot-spots' in the accretion disk---the linear differential equation then governs how the hot spots evolve and dissipate. The impulse-response function of the accretion disk material is given by the Green's function of the linear differential equation. The timescales on which the hot-spots radiate energy is characterized by the powerspectrum of the driving stochastic impulses. We analyze the light curve of the \Kepler AGN Zw 229-15 and find that the observed variability behavior can be modeled as a damped harmonic oscillator perturbed by a colored noise process. The model powerspectrum turns over on time-scale $385$~d. On shorter time-scales, the log-powerspectrum slope varies between $2$ and $4$, explaining the behavior noted by previous studies. We recover and identify both the $5.6$~d and $67$~d timescales reported by previous work. These timescales represent the time-scale on which flux perturbations grow, and the time-scale on which flux perturbations decay back to the steady-state flux level respectively. We make the software package used to study light curves using our method, \textsc{k\={a}l\={i}}, available to the community.

%We have developed and tested a fast software package, \textsc{k\={a}l\={i}}, to analyze light curves using our method that we have made available . 
%We decompose the observed light curve fluctuations into stochastic impulses that drive an ordinary linear differential equation. The Green's function of the differential equation quantifies the time-domain evolution of perturbations to the emitted flux and hence probes dissipative physical processes in accretion flow. The PSD of the stochastic driving impulses characterizes the physical processes responsible for the flux perturbations.
%The PSD of the driving impulses is flat on long time-scales. On time-scales shorter than $1$~d, the impulse PSD begins to rise steeply possibly due to turbulent eddies in the accretion disk, or by the thermal motion of the accretion disk plasma.
\end{abstract}

>>>>

% Enter the current year, for the copyright statements etc.
\pubyear{2017}

@@

% Abstract of the paper
\begin{abstract}
AGN exhibit rapid, high amplitude stochastic flux variability across the entire electromagnetic spectrum on timescales ranging from hours to years. The cause of this variability is poorly understood. We present a method for using variability to (1) measure the time-scales on which flux perturbations evolve and (2) characterize the driving flux perturbations. We model the observed light curve of an AGN as a linear differential equation driven by stochastic impulses. Physically, the impulses could potentially be attributable to local `hot-spots' in the accretion disk---in which case, the linear differential equation describes how the hot spots evolve and dissipate. In this picture, the Green's function of the linear differential equation is the impulse-response function of the accretion disk material to small perturbations of the luminous flux. If accretion disk hot-spots are the root cause of AGN variability, the powerspectrum of the driving stochastic impulses characterizes the timescales on which the hot-spots evolve. We analyze the light curve of the \Kepler AGN Zw 229-15 and find that the observed variability behavior can be modeled as a damped harmonic oscillator perturbed by a colored noise process. The model powerspectrum turns over on time-scale $385$~d. On shorter time-scales, the log-powerspectrum slope varies between $2$ and $4$, explaining the behavior noted by previous studies. We recover and identify both the $5.6$~d and $67$~d timescales reported by previous work. In the local hot-spot picture, these timescales represent the time-scale on which flux perturbations grow, and the time-scale on which flux perturbations decay back to the steady-state flux level respectively. We make the software package used to study light curves using our method, \textsc{k\={a}l\={i}}, available to the community.
\end{abstract}
